Random Forests", OAs

### 2024-06-18 src/oa_RF_corrected.Rmd
corrected RF

df9610 <- read_csv(data.path9610)

@@

df1112 <- read_csv(data.path2011_2012)

df <- bind_rows(df9610, df1112) %>% 
  filter(
    #V1.domain < m,             # for multiple pc
    V1.domain == n,             # for n == 1
    year > 1995 & year <2013) %>%   
  left_join(lookup, by = "pc", suffix =c("","")) %>% 
  group_by(year, oa11cd) %>%
  #summarise(n = n()) %>%            # for multiple pc  
  summarise(n = sum(V1.domain)) %>%  # for n == 1 
  ungroup()

# Partially complete panel as not all OAs have a website in at least one year
df <- df %>% filter(!is.na(oa11cd)) %>% 
  complete(oa11cd, year) %>% 
  replace(is.na(.), 0)

@@

## spatial data OLD

```{r eval=F}
# get OA for England and Wales
path.geo <- paste0(path, "/data/raw/Output_Areas__December_2011__Boundaries_EW_BGC.geojson")
oa.ew <- readOGR(path.geo)
# source: https://geoportal.statistics.gov.uk/

# spatial transformations
oa.ew <- spTransform(oa.ew, CRS("+init=epsg:4326"))

# keep in the data slot only the ONS Output Area id, renaming it as 'id'
oa.ew <- oa.ew[, c('OA11CD', 'Shape__Area')]
colnames(oa.ew@data) <- c('id', 'area')

# reassign the polygon IDs
oa.ew <- spChFIDs(oa.ew, as.character(oa.ew$id))

# check the CRS has changed correctly, and the data slot has shrink to only the ID
summary(oa.ew)

# # get OA for Scotland
# path.geo.sc <- paste0(path, "/data/raw/SG_DataZoneBdry_2011")
# oa.sc <- readOGR(dsn=path.geo.sc, layer = "SG_DataZone_Bdry_2011")
# # source: https://data.gov.uk/dataset/ab9f1f20-3b7f-4efa-9bd2-239acf63b540/data-zone-boundaries-2011
# 
# # spatial transformations
# oa.sc <- spTransform(oa.sc, CRS("+init=epsg:4326"))
# 
# # Scotland (follows same steps as EW, see notes above)
# oa.sc <- oa.sc[, 'DataZone']
# colnames(oa.sc@data) <- c('id')
# 
# # reassign the polygon IDs
# oa.sc <- spChFIDs(oa.sc, as.character(oa.sc$id))
# 
# # check the CRS has changed correctly, and the data slot has shrink to only the ID
# summary(oa.sc)

path.geo.sc <- paste0(path, "/data/raw/output-area-2011-mhw")
oa.sc <- readOGR(dsn=path.geo.sc, layer = "OutputArea2011_MHW")
# source: https://www.nrscotland.gov.uk/statistics-and-data/geography/our-products/census-datasets/2011-census/2011-boundaries

# spatial transformations
oa.sc <- spTransform(oa.sc, CRS("+init=epsg:4326"))

# Scotland (follows same steps as EW, see notes above)
oa.sc <- oa.sc[, c('code', 'SHAPE_1_Ar')]
colnames(oa.sc@data) <- c('id', 'area')

# reassign the polygon IDs
oa.sc <- spChFIDs(oa.sc, as.character(oa.sc$id))

# check the CRS has changed correctly, and the data slot has shrink to only the ID
summary(oa.sc)

# build oa for GB
oa.gb <- maptools::spRbind(oa.ew, oa.sc)
rm(oa.ew, oa.sc)

# oa.gb$geometry <- oa.gb$geometry %>%
#   s2::s2_rebuild() %>%
#   sf::st_as_sfc()

# get GB
path.gb <- "/hdd/internet_archive/archive/gis/Countries_December_2014_Full_Clipped_Boundaries_in_Great_Britain.shp"
gb <- readOGR(path.gb)
# spatial transformations
gb <- spTransform(gb, CRS("+init=epsg:4326"))
```

## spatial data NEW

```{r}
library(sf)

# Get OA for England and Wales
path.geo <- paste0(path, "/data/raw/Output_Areas__December_2011__Boundaries_EW_BGC.geojson")
oa.ew <- st_read(path.geo)

# Spatial transformations
oa.ew <- st_transform(oa.ew, 4326)  # EPSG code for WGS84

# Rename columns and keep only necessary columns
oa.ew <- oa.ew %>% dplyr::select(OA11CD, Shape__Area) %>% 
  rename(id = OA11CD,
         area = Shape__Area)
# oa.ew <- oa.ew[, c('OA11CD', 'Shape__Area')]
# colnames(oa.ew) <- c('id', 'area')

# Check the data structure
print(summary(oa.ew))

# Get OA for Scotland
path.geo.sc <- paste0(path, "/data/raw/output-area-2011-mhw")
oa.sc <- st_read(dsn = path.geo.sc, layer = "OutputArea2011_MHW")

# Spatial transformations
oa.sc <- st_transform(oa.sc, 4326)  # EPSG code for WGS84

# Rename columns and keep only necessary columns
oa.sc <- oa.sc %>% dplyr::select(code, SHAPE_1_Ar) %>% 
  rename(id = code,
         area = SHAPE_1_Ar)
# oa.sc <- oa.sc[, c('code', 'SHAPE_1_Ar')]
# colnames(oa.sc) <- c('id', 'area')

# Check the data structure
print(summary(oa.sc))

@@

# Get GB
path.gb <- "/hdd/internet_archive/archive/gis/Countries_December_2014_Full_Clipped_Boundaries_in_Great_Britain.shp"
gb <- st_read(path.gb)

# Spatial transformations
gb <- st_transform(gb, 4326)  # EPSG code for WGS84
```

@@

### TODELETE

```{r, eval=FALSE}
# ## THIS DROPS L999999... AND NI, WHICH NEEDS TO BE FIXED
# #df <- df %>% filter(!is.na(area)) 
# 
# cities.sf <- st_as_sf(cities, coords = c("long", "lat"))
# cities.sf <- st_set_crs(cities.sf, 4326)
# 
# # help1 <- st_filter(oa.sf, cities.sf) %>% as_tibble %>% dplyr::select(id) %>% 
# #   left_join(df, by = c("id"="oa11cd")) %>% dplyr::select(id, year, n)
# 
# sf_use_s2(FALSE)
# help1 <- st_filter( oa.gb, cities.sf) %>% 
#   #st_coordinates() %>% 
#   as_tibble() %>% 
#   dplyr::select(id) %>% 
#   mutate(cities = c("London",     # The city names have been manually checked and assigned
#                     "Leicester",
#                     "Leeds",
#                     "Sheffield",
#                     "Bristol",
#                     "Birmingham",
#                     "Manchester",
#                     "Liverpool",
#                     "Edinburgh",
#                     "Glasgow"))
# 
# # too slow
# #dist$dist.city.name <- names(dist)[apply(dist[,2:11], MARGIN = 1, FUN = which.min)]
# 
# # This efficiently returns the name of the column with the shortest distance
# dist <- dist %>% mutate(dist.city.name = names(.)[max.col(.[2:11]*-1)+1L])
# 
# help2 <- dist %>% left_join(help1, by = c("dist.city.name" = "cities")) %>% 
#   #rename(nearest.city.oa11cd = id) %>% 
#   dplyr::select(oa11cd, dist.city.name)
# 
# df <- df %>%  left_join(help2, by = c("oa11cd" = "oa11cd")) 
```

@@

### DELETE n for London

```{r, eval=FALSE}

# # OLD London definitions
# # df <- df %>% left_join(df %>% 
# #                          ungroup() %>% 
# #                          filter(oa11cd == "E00176659") %>% 
# #                          dplyr::select(year, n) %>% 
# #                          rename(n.London = n)) %>% 
# #   group_by(oa11cd) %>% 
# #   mutate(n.London.lag = dplyr::lag(n.London)) %>% 
# #   mutate(n.nearest.city.lag = dplyr::lag(n.nearest.city)) %>% 
# #   ungroup() 
# # 
# # london.help <- df %>% group_by(RGN11NM, year) %>% 
# #   summarise(n.London = sum(n)) %>% 
# #   filter(RGN11NM == "London") %>%
# #   mutate(n.London.lag = dplyr::lag(n.London)) %>% 
# #   ungroup() %>% 
# #   dplyr::select(-RGN11NM) 
# 
# london.oa <- st_filter(oa.gb, london.sf %>% 
#                          filter(Name == "Central")) %>% 
#   as_tibble() %>% 
#   dplyr::select(id)
# 
# london.help <- df %>% inner_join(london.oa, by = c("oa11cd" = "id")) %>% 
#   group_by(year) %>% 
#   summarise(n.London = sum(n)) %>% 
#   mutate(n.London.lag = dplyr::lag(n.London)) %>% 
#   ungroup()
# 
# df <- df %>% left_join(london.help, by = c("year" = "year"))
```

@@

path.out <- paste0(path, "/outputs/rf/figures/varimp_OA.png")
ggplot(varimp_mars) + theme_minimal() + labs(x="") #+ theme(panel.background = element_rect(fill = "white"))
ggsave(path.out)

path.out <- paste0(path, "/outputs/rf/models/oa_rf/all_OAs/all_OAs.RData")
save(model.all, file = path.out)

@@

### OLD

```{r, eval=FALSE}
# train on all but one region, test on that region

df.predictions <- data.frame()
for (i in regions){
  for (j in regions[!regions == i]){
    pred <- predict(fit.model.all[names(fit.model.all)==paste0("region_", i)], df[df$RGN11CD==j,])
    pred <- as.data.frame(pred)
    rownames(pred) <- c()
    assign(paste0("region.predict.model.", i, ".on.", j), pred)

    d <- paste0("region.predict.model.", i, ".on.", j)
    d <- cbind(get(d), df %>% filter(RGN11CD==j)) #%>% arrange(year, ladcd)
    d <- d[,c(5, 2, 4, 6, 1)]
    colnames(d)[5] <- "predictions"
    d <- d %>% mutate(trained.on = i)
    df.predictions <- rbind(d, df.predictions)
  }
}

df.predictions <- df.predictions %>% mutate(test.train = paste0(RGN11CD, ".", trained.on))

# split to list by region pair
pred.by.region.all.list <- split(df.predictions, df.predictions$test.train) #correct length = 132 = 12*11

path.lookup <- paste0(path, "/data/raw/Local_Authority_District_to_Region_(April_2021)_Lookup_in_England.csv")  
lookup.region <- read_csv(path.lookup) %>% 
  dplyr::select(RGN21CD, RGN21NM) %>% 
  distinct() %>% 
  rename(RGN11CD = RGN21CD) %>% 
  add_row(RGN11CD = c("Scotland", "N0", "Wales"), 
          RGN21NM = c("Scotland", "Nortern Ireland", "Wales"))

path.out <- paste0(path, "/outputs/rf/heatmap_OA.png")
rf.year.all.metrics %>% 
  as.data.frame() %>%
  rownames_to_column(var = "metrics") %>% 
  pivot_longer(!metrics, names_to = "train.test") %>% 
  pivot_wider(names_from = metrics, values_from = value) %>% 
  separate(train.test, c("train", "test"), remove = F) %>% 
  left_join(lookup.region, by = c("train" = "RGN11CD")) %>% 
  rename(train.region=RGN21NM) %>% 
  left_join(lookup.region, by = c("test" = "RGN11CD")) %>% 
  rename(test.region=RGN21NM) %>% 
  arrange(Rsquared) %>% 
  dplyr::select(train.region, test.region, Rsquared) %>% 
  ggplot(aes(train.region, test.region, fill= Rsquared)) + 
  geom_tile() +
  coord_fixed() +
  labs(y = "", x = "") + #y: test.region, x: train.region
  scale_fill_gradientn(colours = terrain.colors(10), trans = 'reverse') +
  theme(#legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust=1),
        panel.border = element_blank(), 
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "white"))
ggsave(path.out)

  #summarise(r = range(Rsquared))
  #round(2) %>%
  #kable()

## RF

### train on all but one regions

```{r}
# out.path <- paste0(path, "/data/temp/df_for_oa_rf.csv")
# df <- read_csv(out.path)

unregister_dopar <- function() {
  env <- foreach:::.foreachGlobals
  rm(list=ls(name=env), pos=env)
}
unregister_dopar()

# CV
tc <- trainControl(method = "cv",
                   number = 10, #10,
                   allowParallel = T,
                   savePredictions = 'final')

# London region: E12000007

# detectCores()
# cl <- makePSOCKcluster(14)
# registerDoParallel(cl)

# train
start.time <- Sys.time()

set.seed(71)
m.test <- train(n ~ density + area + dist + dist.retail + London +
                  n.slag + year + n.nearest.city, #n.l.slag
                data = df %>% filter(RGN11CD=="E12000008"),
                trControl = tc,
                method = "ranger", #"rf", 
                importance = "impurity",  #TRUE,
                na.action = na.omit)

#stopCluster(cl)
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken #1h

summary(m.test)
plot(m.test)
m.test
print(m.test)

varimp_mars <- varImp(m.test)
plot(varimp_mars, main="Variable Importance")
```

### test on the hold out regions

Wales region is missing!!!

```{r}
pred <- predict(m.test, df %>% ungroup() %>% filter(RGN11CD=="E12000006"), na.action = na.pass)
length(pred)

df %>% ungroup() %>% filter(RGN11CD=="E12000006") %>% filter(if_any(everything(), is.na))

pred <- cbind(pred %>% as_tibble(), df %>% ungroup() %>% filter(RGN11CD=="E12000006"))
postResample(pred = pred$value, obs = pred$n) ## 0.99
```

## RF rolling

### train the model in a loop

```{r}
# Train on t & t + 1

# Make the parallelisation reproducible using https://stackoverflow.com/questions/13403427/fully-reproducible-parallel-models-using-caret. 
# See also https://stackoverflow.com/questions/27944558/set-seed-parallel-random-forest-in-caret-for-reproducible-result

#(8 is the number of tuning parameter, mtry for rf, here equal to ncol(iris)-2)
for(i in 1:10) seeds[[i]]<- sample.int(n=1000, 9) # 9 after adding South

# CV
tc <- trainControl(method = "cv",
                   number = 10,
                   seeds = seeds,
                   allowParallel = T,
                   savePredictions = 'final')

detectCores()
cl <- makePSOCKcluster(6)#14
registerDoParallel(cl)

# run the model for every 2 years
start.time <- Sys.time()
years <- 2001:2012 #1997

for (t in years){

  tplus1 <- t + 1
  set.seed(71)
  print(t)

  model.all <- train(n ~ area + dist + dist.retail + London + south + #growth ~ 
                      n.slag + n.l.slag + n.nearest.city + year, #n.lag +
                     data = df %>% filter(year==t | year==tplus1), #%>% 
                       # mutate(growth = ifelse(growth == -Inf | growth == Inf, NA, growth)) %>% 
                       # mutate(growth = ifelse(is.na(growth), 0, growth)), 
                     #%>% mutate(growth = ifelse(growth== -Inf | growth == Inf, NA, growth))
                     trControl = tc,
                     method = "ranger", 
                     na.action = na.omit,
                     #preProc = c("center", "scale"),
                     importance = 'impurity') #TRUE

  #assign(paste0("model.all",as.character(t + 1)), model.all)
  file <- paste0(path, "/data/temp/oa_rf/timeseries/timeseries", as.character(t + 1), ".RData")
  save(model.all, file = file)
  rm(model.all)
}

stopCluster(cl)
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken

# df %>% filter(growth == Inf) 
# log(n/n.lag)

# The loop creates: 1998 (train on 1997-1998) - 2013 (train on 2012)
# I need: 1998 (train on 1997-1998) - 2011 (train on 2010-2011)
```

```{r}
# create a list of the above model outputs

#load(file = (paste0(path, "/data/temp/oa_rf/timeseries/timeseries2001.RData")))

filenames <- list.files(paste0(path, "/data/temp/oa_rf/timeseries/"), pattern = "*.RData", full.names = T)

t <- 1997
for (i in filenames){
  load(file = i)
  t <- t + 1
  assign(paste0("timeseries",t), model.all)  
}

fit.model.all <- mget(ls(pattern = "^timeseries\\d"))
rm(list = ls(pattern = "^timeseries\\d"))

```{r , include=TRUE, results= 'markup', message=FALSE}
lapply(names(fit.model.all), function(x) plot(varImp(fit.model.all[[x]]), main=as.character(x)))
```

```{r}
help <- lapply(fit.model.all, function(x) varImp(x)) 
help <- lapply(help, function(x) x[[1]])
help <- do.call("rbind", help)

### test

# growth or n

```{r}
## Test on t + 2

# It will create: 2001 (train on 2000-2001) - 2011 (train on 2010)
# I need: 2001 (train on 2000-2001) - 2009 (train on 2008-2009)

# use the model trainned in year t to predict io of year t + 1
years <- (1998:2011)
pred.by.year.all <- data.frame(matrix(NA,nrow=227759, ncol = 0))
for (t in years){
  t_plus_1 <- t + 1
  pred <- predict(fit.model.all[names(fit.model.all)==paste0("timeseries",t)], df[df$year==t_plus_1,])
  pred <- as.data.frame(pred)
  rownames(pred) <- c()
  pred.by.year.all <- cbind(pred.by.year.all, pred)
}

#change column names to match with total
names(pred.by.year.all) <- 1999:2012

# wide to long
pred.by.year.all <- gather(pred.by.year.all,key = year,value = predictions,1:14)

# drop 2000 and select variables form total
df.no1997_1 <- df %>% 
  filter(year!=1996 & year!=1997 & year!=1998) %>% 
  dplyr::select(oa11cd, year, n) # CHANGE n WITH growth

# column bind prediction and data  
pred.by.year.all <- cbind(pred.by.year.all, df.no1997_1 %>% arrange(year, oa11cd)) #DOUBLE CHECK ARRANGE

# pred.by.year to list by year
pred.by.year.all.list <- split(pred.by.year.all, pred.by.year.all$year)

# calculate metrics for every year
rf.year.all.metrics <- lapply(pred.by.year.all.list, function(x) postResample(pred = x$predictions,
                                                                     obs = x$n))  # CHANGE n WITH growth
rf.year.all.metrics %>% as.data.frame() %>%
  round(2) %>%
  kable()

# there are 2 columns named year, so I drop one
pred.by.year.all$year <- NULL

ggplot(data = pred.by.year.all,aes(x = n, y = predictions)) +
  geom_point(colour = "blue") +
  geom_abline(intercept = 0, slope = 1, colour = "red") +
  #geom_vline(xintercept = 23, colour = "green", linetype = "dashed") +
  facet_wrap(~ year,ncol = 2) +
  #coord_cartesian(xlim = c(0,50000),ylim = c(0,50000)) +
  ggtitle("Predicted vs. actual trade by year")
```

## RF spatial

```{r}
df <- df %>% mutate(help = substr(ladcd, start = 1, stop = 2)) %>% 
  mutate(RGN21CD = ifelse(is.na(RGN21CD), help, RGN21CD)) %>% 
  ungroup() %>% 
  dplyr::select(-help)

df <- df %>% dplyr::select(-n.lag)

### train the model in a loop

```{r}
#length is = (n_repeats*nresampling)+1
seeds <- vector(mode = "list", length = 11)

#(8 is the number of tuning parameter, mtry for rf, here equal to ncol(iris)-2)
for(i in 1:10) seeds[[i]]<- sample.int(n=1000, 9) # 9 after adding South

# CV
tc <- trainControl(method = "cv",
                   number = 10,
                   seeds = seeds,
                   allowParallel = T,
                   savePredictions = 'final')

detectCores()
cl <- makePSOCKcluster(14)
registerDoParallel(cl)

# run the model for every 2 years
start.time <- Sys.time()
regions <- df %>% distinct(RGN21CD)
regions <- as.vector(regions$RGN21CD)

for (i in regions){
  set.seed(71)
  model.all <- train(n ~ area + dist + dist.retail + London + south + #growth ~ 
                      n.slag + n.nearest.city + year, #n.lag +  + n.l.slag
                     data = df %>% filter(RGN21CD==i), trControl = tc,
                     method = "ranger",
                     na.action = na.omit,
                     #preProc = c("center", "scale"),
                     importance = 'impurity') #TRUE
  assign(paste0("model.all",as.character(i)), model.all)
}

stopCluster(cl)
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken

# df %>% filter(growth == Inf) 
# log(n/n.lag)

# The loop creates: 1998 (train on 1997-1998) - 2013 (train on 2012)
# I need: 1998 (train on 1997-1998) - 2011 (train on 2010-2011)
```

```{r}
# create a list of the above model outputs
fit.model.all <- mget(ls(pattern = "^model.allE|^model.allN|^model.allW|^model.allS"))

```{r , include=TRUE, results= 'markup', message=FALSE}
lapply(names(fit.model.all), function(x) plot(varImp(fit.model.all[[x]]), main=as.character(x)))
```

```{r}
help <- lapply(fit.model.all, function(x) varImp(x)) 
help <- lapply(help, function(x) x[[1]])
help <- do.call("rbind", help)

### test

# growth or n

```{r}
## Test on t + 2

# train on one region, test on all the rest

df.predictions <- data.frame()
for (i in regions){
  for (j in regions[!regions == i]){
    pred <- predict(fit.model.all[names(fit.model.all)==paste0("model.all",i)], df[df$RGN21CD==j,])
    pred <- as.data.frame(pred)
    rownames(pred) <- c()
    assign(paste0("region.predict.model.", i, ".on.", j), pred)

    d <- paste0("region.predict.model.", i, ".on.", j)
    d <- cbind(get(d), df %>% filter(RGN21CD==j)) #%>% arrange(year, ladcd)
    d <- d[,c(5, 2, 4, 6, 1)]
    colnames(d)[5] <- "predictions"
    d <- d %>% mutate(trained.on = i)
    df.predictions <- rbind(d, df.predictions)
  }
}

df.predictions <- df.predictions %>% mutate(test.train = paste0(RGN21CD, ".", trained.on))

# split to list by region pair
pred.by.region.all.list <- split(df.predictions, df.predictions$test.train) #correct length = 132 = 12*11

path.lookup <- paste0(path, "/data/raw/Local_Authority_District_to_Region_(April_2021)_Lookup_in_England.csv")  
lookup.region <- read_csv(path.lookup) %>% 
  dplyr::select(RGN21CD, RGN21NM) %>% 
  distinct() %>% 
  add_row(RGN21CD = c("S1", "N0", "W0"), RGN21NM = c("Scotland", "Nortern Ireland", "Wales"))

rf.year.all.metrics %>% 
  as.data.frame() %>%
  add_rownames(var = "metrics") %>% 
  pivot_longer(!metrics, names_to = "train.test") %>% 
  pivot_wider(names_from = metrics, values_from = value) %>% 
  separate(train.test, c("train", "test"), remove = F) %>% 
  left_join(lookup.region, by = c("train" = "RGN21CD")) %>% 
  rename(train.region=RGN21NM) %>% 
  left_join(lookup.region, by = c("test" = "RGN21CD")) %>% 
  rename(test.region=RGN21NM) %>% 
  arrange(Rsquared)
  #summarise(r = range(Rsquared))
  #round(2) %>%
  #kable()
```

### test plots

```{r}
#plots
ggplot(data = df.predictions, aes(x = n, y = predictions)) +
  geom_point(colour = "blue") +
  geom_abline(intercept = 0, slope = 1, colour = "red") +
  #geom_vline(xintercept = 23, colour = "green", linetype = "dashed") +
  facet_wrap(~ test.train, ncol = 2) +
  #coord_cartesian(xlim = c(0,50000),ylim = c(0,50000)) +
  ggtitle("Predicted vs. actual trade by year")
```

>>>>

df9610 <- read_csv(data.path9610) %>% 
  filter(
      #V1.domain < m,             # for multiple pc
      V1.domain == n,             # for n == 1
      year > 1995)

# df9610 %>% filter(V1.domain == 1) %>% 
#   left_join(lookup, by = "pc", suffix =c("","")) %>% 
#   filter(ladcd == "E08000006" & year == 2006) %>% 
#   group_by(pc) %>% 
#   summarise(n = n()) %>% 
#   arrange(desc(n))
# 
# df9610 %>% filter(pc == "M28 2SL" & year == 2006 & V1.domain == 1)

problem.pcs <- df9610 %>% filter(year > 1999 & year < 2011) %>% 
  group_by(pc, year) %>% 
  summarise(n = n()) %>%
  ungroup() %>% 
  # complete(pc, year) %>% 
  # replace(is.na(n), 0) %>% 
  arrange(desc(n)) %>% 
  pivot_wider(names_from = year, values_from = n, names_prefix = "n_") %>% 
  dplyr::select(pc, n_2000, n_2001, n_2002, n_2003, n_2004, n_2005, n_2006, n_2007, n_2008, n_2009, n_2010) %>% 
  slice_head(n=10) %>% 
  dplyr::select(pc)

# [1] "M28 2SL"  "SE24 9HP" "CV8 2ED"  "CW1 6GL"  "EC1V 4PY" "DE21 7BF" "E14 9SR"  "GL16 7YA" "WC1N 3XX"
# [10] "CB2 1AB" 
```

## Correct 1996-2010

The above exploratory analysis indicated that there is a huge increase in 2004-2006
in the above postcodes. I turn them to NAs and then use a regression to impute these
gaps.

```{r}
df9610 <- df9610 %>% 
  group_by(pc, year) %>% 
  summarise(n = n()) %>% 
  ungroup() %>% 
  mutate(n = ifelse(pc %in% as.character(problem.pcs$pc) & year > 2003 & year <2007, NA, n))

df9610 <- pdata.frame(df9610)
predictions <- round(predict(plm(n ~ as.factor(year), effect = "individual", 
                                 model = "within", data = df9610), newdata = df9610), 2)

df9610$n[is.na(df9610$n)] <- predictions[is.na(df9610$n)]
df9610 %>% filter(pc == "M28 2SL") %>% distinct(year)
```

## Load remaining data

```{r}
df9610 <- as_tibble(df9610) %>% 
  mutate(year = as.double(as.character(year))) %>% 
  left_join(lookup, by = "pc", suffix =c("","")) %>%
  group_by(year, oa11cd) %>%
  summarise(n = n()) %>%            
  ungroup()

@@

df1112 <- read_csv(data.path2011_2012) %>% 
  filter(
    #V1.domain < m,             # for multiple pc
    V1.domain == n,             # for n == 1
    year > 1995 & year <2013) %>%   
  left_join(lookup, by = "pc", suffix =c("","")) %>% 
  group_by(year, oa11cd) %>%
  summarise(n = n()) %>%             # for n == 1  
  #summarise(n = sum(V1.domain)) %>% # for multiple pc  
  ungroup()

df <- bind_rows(df9610, df1112) %>% 
  filter(!is.na(oa11cd)) %>% 
  complete(oa11cd, year) %>% 
  replace(is.na(.), 0)

@@

## spatial data

```{r}
# get OA for England and Wales
path.geo <- paste0(path, "/data/raw/Output_Areas__December_2011__Boundaries_EW_BGC.geojson")
oa.ew <- st_read(path.geo)
# source: https://geoportal.statistics.gov.uk/

# spatial transformations
oa.ew <- st_transform(oa.ew, 4326)  # EPSG code for WGS84

# keep in the data slot only the ONS Output Area id, renaming it as 'id'
oa.ew <- oa.ew %>% 
  dplyr::select(OA11CD, Shape__Area) %>% 
  rename(id = OA11CD,
         area = Shape__Area)

path.geo.sc <- paste0(path, "/data/raw/output-area-2011-mhw")
oa.sc <- st_read(dsn=path.geo.sc, layer = "OutputArea2011_MHW")
# source: https://www.nrscotland.gov.uk/statistics-and-data/geography/our-products/census-datasets/2011-census/2011-boundaries

# spatial transformations
oa.sc <- st_transform(oa.sc, 4326)  # EPSG code for WGS84

# Scotland (follows same steps as EW, see notes above)
oa.sc <- oa.sc %>% 
  dplyr::select(code, SHAPE_1_Ar) %>% 
  rename(id = code,
         area = SHAPE_1_Ar)

@@

# get UK
path.uk <- "https://services1.arcgis.com/ESMARspQHYMw9BZ9/arcgis/rest/services/Countries_December_2023_Boundaries_UK_BUC/FeatureServer/0/query?outFields=*&where=1%3D1&f=geojson"
uk <- st_read(path.uk)
# spatial transformations
uk <- st_transform(uk, 4326)  # EPSG code for WGS84
```

@@

@@

@@

path.out <- paste0(path, "/outputs/rf/figures/varimp_OA_corrected.png")
ggplot(varimp_mars) + theme_minimal() + labs(x="") #+ theme(panel.background = element_rect(fill = "white"))
ggsave(path.out)

path.out <- paste0(path, "/outputs/rf/models/oa_rf/all_OAs/all_OAs_corrected.RData")
save(model.all, file = path.out)

path.out <- paste0(path, "/outputs/rf/figures/varimp_OA_corrected.csv")
write_csv(varimp_mars, path.out)

@@
